Time Series Bootstrapping For Solar Current

### 2021-12-15 deliverables/paper.Rmd
Added figures and tables, reorganized

---
title: "Time Series Bootstrapping For Solar Current"
author: "Evan Kessler, Adam Kiehl, and Boston Lee"
date: "2021/12/16"
output: pdf_document
bibliography: references.bib
---

@@

```{r libs, include=FALSE, message=FALSE}
# Import packages
library(knitr)
library(tidyverse)
library(boot)
```

@@

# EDA

@@

@@

```{r, include=FALSE}
# rough MC coverage estimate assuming dependent bootstrap distribution as a null
B <- 10000
n <- nrow(boot_block_df)

lower <- as.numeric(iid_ci[1])
upper <- as.numeric(iid_ci[2])

mu <- mean(boot_block_df$boot)
sigma <- sd(boot_block_df$boot)

sample <- rnorm(B, mu, sigma)

sum(sample >= lower & sample <= upper) / n
```

>>>>

---
title: "Time Series Bootstrapping For Solar Current"
author: "Evan Kessler, Adam Kiehl, and Boston Lee"
date: "2021/12/16"
output: bookdown::pdf_document2
bibliography: references.bib
---

@@

```{r libs, include=FALSE, message=FALSE}
# Import packages
library(knitr)
library(bookdown)
library(tidyverse)
library(boot)
```

```{r knitr-opts}
knitr::opts_chunk$set(fig.pos = "t", fig.align = 'center', out.width = "75%", out.extra = "")
```

@@

@@

## Bootstrapping

## Descriptive Statistics

```{r ghi-ts, fig.cap="Time series of GHI values for the first six days in the dataset", echo=FALSE}
print(time_series_ghi)
```

```{r current-ts, fig.cap="Time series of simulated current values for the first six days in the dataset.", echo=FALSE}
print(time_series_current)
```

```{r ghi-hour-boxplot, fig.cap="Distribution of GHI at each hour for the entire unfiltered dataset.", echo=FALSE}
print(hour_plot_ghi)
```

```{r current-hour-boxplot, fig.cap="Distribution of GHI at each hour for the entire unfiltered dataset.", echo=FALSE}
print(hour_plot_current)
```

## Bootstrapping

@@

```{r mean-boot-plot, fig.cap="Distributions of bootstrap mean simulated current for both iid and block bootstrapping methods. Percentile 95 percent bootstrap confidence intervals for mean simulated current overlayed.", echo=FALSE}
print(mean_boot_plot)
```

```{r bootstrap-ci, echo=FALSE}
bootstrap_ci_table <- rbind(
c("iid", paste("(", round(iid_ci[1],3),",", round(iid_ci[2],3), ")")),
c("Block", paste("(", round(block_ci[1],3),",", round(block_ci[2], 3), ")"))
)
colnames(bootstrap_ci_table) <- c("Bootstrap Method", "95% CI")
rownames(bootstrap_ci_table) <- c()

bootstrap_ci_table %>% kable(booktabs = TRUE,
caption="95% confidence intervals for the mean simulated current, as generated by each of the two bootstrapping methods.")
